The POSIX time standard

### 2023-02-21 src/check_links.Rmd
Reformatted tags in yaml headers

```{r read_old}
html_path <- "c:/Users/simons/Dropbox/professional/fun stuff/update-website/"
html_path <- "c:/Users/steve/Dropbox/professional/fun stuff/update-website/"
html_pattern <- "html$"
md_path <- "../text/"
md_pattern <- "md$"
subdir_list=c("99", paste0("0", 0:9), 10:22)
md_files <- NULL
html_files <- NULL
for (yr in rev(subdir_list)) {
  print(yr)

>>>>

```{r read_old}
html_path <- "c:/Users/steve/Dropbox/professional/fun stuff/update-website/"
html_path <- "c:/Users/simons/Dropbox/professional/fun stuff/update-website/"
html_pattern <- "html$"
md_path <- "../text/"
md_pattern <- "md$"
subdir_list=c("99", paste0("0", 0:9), 10:22)
md_files <- NULL
html_files <- NULL
for (yr in rev(subdir_list)) {
  print(yr)

### 2023-02-21 src/year-end-summary.Rmd
Reformatted tags in yaml headers

# pad single digits with leading zero
zpad <- function(x) {
  ifelse(nchar(x)==1, paste0("0", x), x)
}
```

@@

```{r}
# Put it all together
yyyy_list <- c(1999:2023)
n_problems <- 0
n_files <- 0
for (yyyy in yyyy_list) {
  yy <- str_sub(yyyy, 3, 4)
  output_file <- glue("text/{yy}/{yyyy}.md")
  glue("text/{yy}") %>%
    list.files %>%
    str_subset("md$") -> f
  problem_files <- NULL
  date_list <- NULL
  for (fn in f) {
    file_text <- read_lines(glue("text/{yy}/{fn}"))
    problem_files %<>% append(check_source(file_text))
    date_list %<>% append(check_date(file_text))
  }

@@

  if (n_year > 0) {print(problem_files)}

  print("Check 1")
  unlink(output_file)
  # file.remove(output_file)
  print("Check 2")
  create_yaml(yyyy) %>% write_lines(output_file)
  print("Check 3")
  write_lines(" ", output_file, append=TRUE)

@@

  problem_files %>% write_lines(output_file, append=TRUE)
  # write_lines(" ", output_file, append=TRUE)

>>>>

# pad single digits with leading zero
zpad <- function(x) {
  ifelse(nchar(x)==1, paste0("0", x), x)
}

update <- FALSE
print("Check 1")
```

@@

```{r}
# Put it all together
yyyy_list <- c(1999:2023)
n_problems <- 0
n_files <- 0
for (yyyy in yyyy_list) {
  cat("\n")
  cat(yyyy)
  cat("\n\n")
  yy <- str_sub(yyyy, 3, 4)
  output_file <- glue("../text/{yy}/{yyyy}.md")
  glue("../text/{yy}") %>%
    list.files %>%
    str_subset("md$") -> f
  problem_files <- NULL
  date_list <- NULL
  for (fn in f) {
    file_text <- read_lines(glue("../text/{yy}/{fn}"))
    problem_files %<>% append(check_source(file_text))
    date_list %<>% append(check_date(file_text))
  }

@@

  if (n_year > 0) {print(problem_files)}
  print(problem_files)

  if (update==FALSE) {next}

  create_yaml(yyyy) %>% write_lines(output_file)
  write_lines(" ", output_file, append=TRUE)

@@

  problem_files %>% write_lines(output_file, append=TRUE)

### 2023-02-21 text/04/early-stopping-animal.Rmd
Reformatted tags in yaml headers

---
title: Early stopping in an animal study
author: Steve Simon
date: 2004-07-01
categories:
- Blog post
tags:
- Early stopping
output: html_document
---
I was helping someone with power calculations for an animal experiment.
There were several ways to estimate power and they all seemed to point
to the use of either 8 animals per group or 12 animals per group. I
explained that if she was more risk averse, she should use 12 animals
and if she were more work averse, she should use 8 animals. Her answer
surprised me a bit. She said that she liked the idea of using 12 animals
per group. That way, if the results achieved significance after only 8
animals, she could go back to the Animal Care and Use Committee and tell
that she saved a few animals.

@@

Ludbrook J. Interim analyses of data as they accumulate in laboratory
experimentation. BMC Med Res Methodol 2003: 3(1); 15.
[Medline](http://www.ncbi.nlm.nih.gov/entrez/query.fcgi?cmd=Retrieve&db=PubMed&list_uids=12930561&dopt=Abstract)
[Abstract](http://www.biomedcentral.com/1471-2288/3/15/abstract)
Avialable in [html format](http://www.biomedcentral.com/1471-2288/3/15)
or [pdf format](http://www.biomedcentral.com/content/pdf/1471-2288-3-15.pdf)

@@

You can find an [earlier version](http://www.pmean.com/04/EarlyStoppingAnimal.html) of this page on my [original website](http://www.pmean.com/original_site.html).

>>>>

---
title: Early stopping in an animal study
author: Steve Simon
date: 2004-07-01
categories:
- Blog post
tags:
- Early stopping
output: html_document
---

I was helping someone with power calculations for an animal experiment. There were several ways to estimate power and they all seemed to point to the use of either 8 animals per group or 12 animals per group. I explained that if she was more risk averse, she should use 12 animals and if she were more work averse, she should use 8 animals. Her answer surprised me a bit. She said that she liked the idea of using 12 animals per group. That way, if the results achieved significance after only 8 animals, she could go back to the Animal Care and Use Committee and tell that she saved a few animals.

@@

Ludbrook J. Interim analyses of data as they accumulate in laboratory experimentation. BMC Med Res Methodol 2003: 3(1); 15. Available in [html format](http://www.biomedcentral.com/1471-2288/3/15) or [pdf format](http://www.biomedcentral.com/content/pdf/1471-2288-3-15.pdf)

@@

You can find an [earlier version][sim1] of this page on my [original website][sim2].

[sim1]: http://www.pmean.com/04/EarlyStoppingAnimal.html
[sim2]: http://www.pmean.com/original_site.html

### 2023-02-21 text/14/axis.Rmd
Reformatted tags in yaml headers

---
title: "Some simple examples of manipulating the axes in a graph"
author: "Steve Simon"
source: "http://www.pmean.com/axis.html"
date: "2014-01-01"
category: Blog post
tags: Sample size
output: html_document
---

>>>>

---
title: "Some simple examples of manipulating the axes in a graph"
author: "Steve Simon"
source: "http://www.pmean.com/axis.html"
date: "2014-01-01"
category: Blog post
tags:
- Sample size justification
output: html_document
---

### 2023-02-21 text/15/difference-of-two-exponentials.Rmd
Reformatted tags in yaml headers

---
title: "PMean: Nonlinear regression for the difference of two exponentials"
author: "Steve Simon"
source: "http://blog.pmean.com/difference-of-two-exponentials/"
date: "2015-10-05"
category: 
- Blog post
tags: 
- incomplete page
- nonlinear regression
- R software
output: html_document
---

>>>>

---
title: "Nonlinear regression for the difference of two exponentials"
author: "Steve Simon"
source: "http://blog.pmean.com/difference-of-two-exponentials/"
date: "2015-10-05"
category: 
- Blog post
tags:
- incomplete page
- nonlinear regression
- R software
output: html_document
---

### 2023-02-21 text/15/missing-values-in-r.Rmd
Reformatted tags in yaml headers

---
title: "PMean: Missing values in R talk"
author: "Steve Simon"
source: "http://blog.pmean.com/missing-values-in-r/"
date: "2015-02-07"
category: Blog post
tags: R software
output: html_document
---

>>>>

---
title: "Missing values in R talk"
author: "Steve Simon"
source: "http://blog.pmean.com/missing-values-in-r/"
date: "2015-02-07"
category:
- Blog post
tags:
- R software
output: html_document
---

### 2023-02-21 text/15/relationships-in-r.Rmd
Reformatted tags in yaml headers

---
title: "PMean: Examining relationships in R"
author: "Steve Simon"
source: "http://blog.pmean.com/relationships-in-r/"
date: "2015-04-03"
categories:
- Blog post
tags:
- R software
output: html_document
---

>>>>

---
title: "Examining relationships in R"
author: "Steve Simon"
source: "http://blog.pmean.com/relationships-in-r/"
date: "2015-04-03"
categories:
- Blog post
tags:
- R software
output: html_document
---

### 2023-02-21 text/22/analysis-of-means.Rmd
Reformatted tags in yaml headers

---
title: "A second alternative to the pairwise testing approach"
author: "Steve Simon"
date: '2022-07-04'
output:
  html_document: default
category: Blog post
tags: Analysis of means
source: new
---

>>>>

---
title: "A second alternative to the pairwise testing approach"
author: "Steve Simon"
date: '2022-07-04'
output:
  html_document: default
category: Blog post
tags:
- Analysis of means
source: new
---

### 2023-02-21 text/22/box-with-no-whiskers.Rmd
Reformatted tags in yaml headers

---
title: "My boxplot shows a box but no whiskers"
author: "Steve Simon"
date: '2022-12-15'
output:
  html_document: default
category: Blog post
tags: Graphical display
source: new
---

>>>>

---
title: "My boxplot shows a box but no whiskers"
author: "Steve Simon"
date: '2022-12-15'
output:
  html_document: default
category: Blog post
tags:
- Graphical display
source: new
---

### 2023-02-21 text/22/definition-schoenfeld-residuals.Rmd
Reformatted tags in yaml headers

---
title: "Schoenfeld residuals"
author: "Steve Simon"
date: '2022-11-30'
output:
  html_document: default
category: Blog post
tags: Survival analysis
source: new
---

>>>>

---
title: "Schoenfeld residuals"
author: "Steve Simon"
date: '2022-11-30'
output:
  html_document: default
category: Blog post
tags:
- Survival analysis
source: new
---

### 2023-02-21 text/22/dunnetts-test.Rmd
Reformatted tags in yaml headers

---
title: "Dunnett's test"
author: "Steve Simon"
date: '2022-07-04'
output:
  html_document: default
category: Blog post
tags: Analysis of means
source: new
---

>>>>

---
title: "Dunnett's test"
author: "Steve Simon"
date: '2022-07-04'
output:
  html_document: default
category: Blog post
tags:
- Analysis of means
source: new
---

### 2023-02-21 text/22/posix-time.Rmd
Reformatted tags in yaml headers

---
title: "The POSIX time standard"
author: "Steve Simon"
date: "2022-11-12"
output:
  html_document: default
category: Blog post
tags: Data science
source: new
---

>>>>

---
title: "The POSIX time standard"
author: "Steve Simon"
date: "2022-11-12"
output:
  html_document: default
category: Blog post
tags:
- Data science
source: new
---
